\documentclass[11pt,a4paper]{letter}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}

\signature{[First Author, PhD/MD]\\
[Corresponding Author]\\
[Department], [Institution]\\
\url{first.author@institution.edu}}

\begin{document}

\begin{letter}{%
The Editor-in-Chief\\
\textit{Journal of King Saud University - Computer and Information Sciences}\\
King Saud University\\
Riyadh, Saudi Arabia}

\opening{Dear Editor,}

We are pleased to submit our manuscript entitled \textbf{``MDT-LLM:
A Multidisciplinary Team-Based Multi-Agent Large Language Model
Framework with Retrieval-Augmented Generation for Evidence-Based
Clinical Decision Support''} for consideration in the
\textit{Journal of King Saud University --- Computer and Information
Sciences}.

This work presents the first systematic factorial benchmarking of
multi-agent LLM orchestration combined with retrieval-augmented
generation (RAG) on complex clinical decision-making tasks. Our
contributions are four-fold:

\begin{enumerate}
\item \textbf{A novel multi-agent framework} (\textsc{MDT-LLM}) that
simulates the role composition and synthesis structure of a clinical
multidisciplinary team (MDT), coupled with a RAG pipeline over the
current NCCN guidelines.

\item \textbf{A new benchmark} (\textsc{LungMDT-Bench-100}) of 100
expert-annotated lung-cancer clinical scenarios across 6 clinical
domains and 3 difficulty levels, accompanied by guideline-concordant
gold-standard answers.

\item \textbf{A cross-provider multi-judge LLM-as-judge protocol} with
explicit inter-judge reliability reporting (Cohen's weighted $\kappa$),
applicable beyond our specific domain.

\item \textbf{Counter-intuitive empirical findings.} We show that naive
RAG \emph{reduces} output quality in strong LLMs (Claude Sonnet 4.5
$\Delta{=}{-}0.29$ and DeepSeek R1 $\Delta{=}{-}0.32$, both
Bonferroni-corrected $p<0.002$, medium effect size), a finding robust
across retrieval depths $k \in \{1, 3, 5, 10\}$. We further show that a
\emph{heterogeneous} multi-agent configuration, mixing four different
LLMs across four specialist roles, achieves performance parity with
the best homogeneous configuration at approximately 32\% lower cost.
\end{enumerate}

We believe this work aligns well with \textit{JKSUCIS}'s scope, which
spans foundational and applied advances in computer and information
sciences including artificial intelligence, machine learning, and
medical informatics. Our multi-agent system design and evaluation
methodology represent substantive methodological contributions to the
field of applied large language models in high-stakes domains.

\textbf{Originality and exclusivity.} This manuscript has not been
published previously and is not under consideration elsewhere. All
authors have approved the submission. We have no conflicts of
interest to disclose.

\textbf{Reproducibility.} The full benchmark, framework
implementation, judge score CSVs, and analysis scripts are released
as open-source artifacts accompanying this submission.

\textbf{Suggested reviewers} (at the Editor's discretion):

\begin{itemize}
\item Prof.\ [Name], [Institution] --- expert in clinical NLP and
  medical LLM evaluation.
\item Dr.\ [Name], [Institution] --- expert in multi-agent systems
  and LLM orchestration.
\item Prof.\ [Name], [Institution] --- expert in retrieval-augmented
  generation for knowledge-intensive tasks.
\end{itemize}

Thank you for considering our work. We look forward to your decision.

\closing{Sincerely,}

\end{letter}

\end{document}
